% !TeX spellcheck = en_GB
\phantomsection
\addcontentsline{toc}{chapter}{Statement of Contributions}
\begin{center}\textbf{Statement of Contributions}\end{center}

Andreas Stöckel is the sole author of Chapters 1, 4, and 6.
These chapters were either not written for publication or are based on self-published technical reports.
The remaining chapters are, in heavily edited and extended form, based on the following published works:

\begin{enumerate}
	\item[{[1]}] \fullcite{stoeckel2021}
	\item[{[2]}] \fullcite{stockel2021connecting}
\end{enumerate}

\noindent Use of these publications in this thesis is with permission of the publishers.
All figures in this thesis, with the sole exception of \Cref{fig:izhikevich_whichmod_figure1}, were created by the author.
Annotations such as \enquote{inspired by} or \enquote{adapted from} merely indicate the source of the presented information.

\subsubsection{Contributions to the individual publications}

\begin{enumerate}
	\item[{[1]}] This research was conducted by Andreas Stöckel.
	Chris Eliasmith supervised this work and helped designing the experiments.
	Andreas Stöckel wrote all the underlying code, conducted the experiments, created the figures, and wrote the manuscript.
	Chris Eliasmith edited the manuscript.
	\item[{[2]}] This research was conducted by Andreas Stöckel and Terrence C.~Stewart.
	Andreas Stöckel was responsible for conducting the experiments, contributing the underlying theoretical work, writing, creating all figures, and conducting the literature review.
	Terrence C.~Stewart helped with designing the final network, exploring the parameter space, and writing the paper.
	Chris Eliasmith supervised this work, provided helpful feedback, and edited the manuscript.
\end{enumerate}

\subsubsection{Use of these publications in this thesis}

\begin{description}
	\item[\normalfont\emph{Chapter~2:}] Small parts of this chapter are based on [1], in particular the description of the Neural Engineering Framework in Sections~2.3.3-2.3.5.
	\item[\normalfont\emph{Chapter~3:}] The introduction of Chapter~3, and Sections 3.2-3.4, 3.6 are in part based on [1].
	The experiments in Section 3.3 and 3.4 and the corresponding figures are, with minor changes, as previous published.
	\item[\normalfont\emph{Chapter~4:}] This chapter is in large parts based on [2].
\end{description}

\clearpage
