\chapter{Mathematical Notation and Reference}
\label{app:mathematical_notation}

\begin{PriorPublication}
This appendix, in particular \Cref{app:linear_algebra}, is partially based on material previously published as a technical report \citep{stockel2021discrete}.
\end{PriorPublication}

Some care has been taken to make the mathematical notation in this thesis as consistent as possible.
Unfortunately, as this thesis covers material from different disciplines, the notation chosen here may not be exactly what a reader coming from a specific discipline might expect.
The goal of this appendix is to clarify our notation and to provide a reference for some basic mathematical concepts that we did not want to include in the main text.

\section{Notational conventions}

\begin{table}
\centering
\caption{Typographical conventions used to denote different mathematical objects.}
\label{tbl:typography}
\small
\begin{tabular}{p{4cm} p{3cm} p{7.5cm}}
	\toprule
	\emph{Symbols} & \emph{Objects} & \emph{Description} \\
	\midrule
	$d$, $i$, $j$, $k$, $\ell$, $m$, $n$, $M$, $N$ & Integers & By convention, these symbols denote integers, typically used as index variables or to denote cardinalities. \\
	\midrule
	$a$, $f$, $g$, $u$, $v$, $x$, $y$, $\ldots$ \newline $\alpha$, $\beta$, $\gamma$, $\ldots$ \newline $G$, $H$, $J$, $\ldots$ & \raggedright Scalars and functions & All other italic letters (Greek or Latin) denote scalars, usually elements of the real number-line \Reals. Alternatively, these letters are used to denote functions, including probability variables.\\
	\midrule
	$\vec a$, $\vec b$, $\vec u$, $\vec x$, $\vec y$, $\vec z$, $\ldots$ & \raggedright Vectors and some vector\--valued functions & Bold, lower-case Latin letters denote column vectors, typically elements of the $d$-dimensional real vector space $\Reals^{n}$. Alternatively, these letters may denote vector-valued functions to explicitly disambiguate between scalar and vector-valued functions.\\
	\midrule
	$\tmp a$, $\tmp b$, $\tmp u$, $\tmp x$, $\tmp y$, $\tmp z$, $\ldots$ & \raggedright Functions over time & Lowercase Latin letters in Fraktur script are used to explicitly denote real- or vector-valued functions over time.
	To improve readability, we only use this notation if it is necessary to disambiguate between temporal and non-temporal quantities.\\
	\midrule
	$\mat A$, $\mat B$, $\mat C$, $\mat D$, $\ldots$ \newline
	$\mat \Upsilon$, $\mat \Gamma$, $\ldots$ & Matrices & Bold upper-case Greek or Latin letters denote matrices $\Reals^{m \times n}$. \\
	\midrule
	$\mathbb{B}$, $\mathbb{N}$, $\mathbb{R}$, $\mathbb{S}$, $\mathbb{Q}$, $\mathbb{X}$, $\ldots$ & Sets & Double-struck uppercase Latin letters denote sets, i.e., collections of mathematical objects. \\
	\midrule
	$\mathcal{G}$, $\mathcal{H}$, $\ldots$ & Special symbols & Other symbols, such as calligraphic letters are used sparsely throughout this document for further disambiguation.\\ 
	\bottomrule
\end{tabular}
\end{table}

We follow the typographical guidelines outlined in \Cref{tbl:typography}.
Symbols used throughout this document follow 

\section{Linear Algebra}
\label{app:linear_algebra}

The purpose of this section is to provide a quick reference for some terms from linear algebra that are used throughout this document.
Of course, this appendix cannot provide a comprehensive introduction to linear algebra.
In particular, we will---for brevity---assume that our vector spaces are always $\mathbb{R}^d$ with scalar elements from $\mathbb{R}$.
Readers wishing to learn more about linear algebra are referred to the excellent and freely available introductory book by \citet{hefferon2020linear}.

\begin{definition}[Linear function]
A \emph{linear function} is a function $f : \Reals^n \longrightarrow \Reals^{m}$ that fulfills the following property
\begin{align*}
	f(a \vec x + b \vec y) &= a f(\vec x) + b f(\vec y) \quad \quad \text{for all } \vec x, \vec y \in \mathbb{R}^n\,, a, b \in \mathbb{R} \,.
\end{align*}
\end{definition}

\begin{definition}[Matrix]
A \emph{matrix} $\mat A$ is a member of the set of all possible linear functions mapping $\Reals^n$ onto $\Reals^m$.
All matrices can be represented as a grid of $m \times n$ real numbers.
\begin{align*}
	\mat A = \begin{pmatrix}
		a_{1, 1} & \ldots & a_{1, n} \\
		\vdots & & \vdots \\
		a_{m, 1} & \ldots & a_{m, n}
	\end{pmatrix} \,,
\end{align*}
\end{definition}

\subsubsection{Matrices as linear functions}
Matrices over a vector space are defined as spanning the set of all possible linear operators.
That is, if $f : \Reals^n \longrightarrow \Reals^m$ is 

The choice of the number of rows $m$ and columns $n$ in a matrix may sometimes seem arbitrary.
Where possible, we use the following convention.
A $\mat A \in \Reals^{m \times n}$ can be seen as a linear operator mapping from $\Reals^{n}$ onto $\Reals^{m}$.


\section{Functional Analysis}
\label{app:functional_analysis}